---
title: "Sung Lee Final Project"
author: "Sung Lee"
date: "1/17/2020"
output: 
 html_document: 
 df_print: paged
---
[Final Assignment on RPubs](http://rpubs.com/logicalschema/r_final_project "Sung's Final Project Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/r_winter_projects/blob/master/finalproject.Rmd "Sung's Final Project Assignment Github")


1. Data Exploration: This should include summary statistics, means, medians, quartiles, or any other relevant information about the data set. Please include some conclusions in the R Markdown text.

``` {r}
require(plyr)
require(ggplot2)


gssData <- read.csv('GSSvocab.csv',header=TRUE, sep=",")
summary(gssData)

```

Conclusions: Some conclusions from the data: 1) the percentage of women who participated in the study was `r round((16385/(12482 + 16385))* 100, 2)` percent and 2) the number of participants who identified as native born was 26,224 in comparison with no's: 2,556 and NA's: 87.
<br><br>
2. Data wrangling: Please perform some basic transformations. They will need to make sense but could include column renaming, creating a subset of the data, replacing values, or creating new columns with derived data (for example – if it makes sense you could sum two columns together)

```{r}
#Renaming the columns for the data set
gssData <- rename(gssData, c("year" = "Year", "gender" = "Gender", "educGroup" = "EducationGroup", "vocab" = "VocabularyScore", "age" = "Age", "educ" = "Education", "ageGroup" = "AgeGroup", "nativeBorn" = "NativeBorn"))

#Creating a subset for the data for participants between 21 and 50 years of age
subset_gssData <- subset(gssData, Age >= 21 & Age <= 50)
head(subset_gssData, 5)
```
3. Graphics: Please make sure to display at least one scatter plot, box plot and histogram. Don’t be limited to this. Please explore the many other options in R packages such as ggplot2.

```{r}
# scatter plot
plot(gssData$Education,gssData$VocabularyScore, xlab='Years of Education',ylab='Vocabulary Score' ,main='Years of Education vs. Vocabulary Score', col='blue')

# box plot
boxplot(Education~VocabularyScore,data=gssData, main="Education and Vocabulary Score", xlab="Education", ylab="Vocabulary Score") 

#histogram

ggplot(gssData, aes(x=VocabularyScore, color=NativeBorn)) + geom_histogram(fill="white", bins=10)


```
