---
title: "Week 2 Assignment"
author: "Sung Lee"
date: "1/9/2020"
output: html_document
---
``` {r}
require(plyr)

# Load data: Temporarily using the local file until completion
# US Births in 1969 - 1988 
#csv_url <- "https://raw.githubusercontent.com/logicalschema/r_winter_projects/master/Birthdays.csv"
csv_url <- "Birthdays.csv"
birthday_data <- read.table(file = csv_url, header = TRUE, sep = ",")
head(birthday_data, 3)
```
<br>
1. Use the summary function to gain an overview of the data set. Then display the mean and median for at least two attributes.

```{r}
summary(birthday_data)
```

###### The mean and median for the month attribute
```{r}
mean(birthday_data$month)
median(birthday_data$month)
```

###### The mean and median for the births attribute
```{r}
mean(birthday_data$births)
median(birthday_data$births)
```
<br>
2. Create a new data frame with a subset of the columns and rows. Make sure to rename it.
```{r}
subset_birthdays = subset(birthday_data, state == "NY" & year >= 1981 & year <= 1988, select=c(year, month, births))

tail(subset_birthdays, 3)
```

<br>
3. Create new column names for the new data frame.

```{r}
subset_birthdays <- rename(subset_birthdays, c("year" = "Y", "month" = "M", "births" = "BIRTHS"))

head(subset_birthdays, 3)
```
<br>
4. Use the summary function to create an overview of your new data frame. Then print the mean and median for the same two attributes. Please compare.

``` {r}
summary(subset_birthdays)
mean(subset_birthdays$M)
median(subset_birthdays$M)
mean(subset_birthdays$BIRTHS)
median(subset_birthdays$BIRTHS)

```

The month attribute did not vary. However, the births attribute varied widely from the original data set. The original had a mean: 189 and median: 129. The subset data taken for New York between 1981 and 1988 produced a mean: 709 and median: 711.

<br>
5. For at least 3 values in a column please rename so that every value in that column is renamed. For example, suppose I have 20 values of the letter “e” in one column. Rename those values so that all 20 would show as “excellent”.

<br>
6. Display enough rows to see examples of all of steps 1-5 above.


<br>
7. BONUS – place the original .csv in a github file and have R read from the link. This will be a very useful skill as you progress in your data science education and career.

```{r eval=FALSE}
csv_url <- "https://raw.githubusercontent.com/logicalschema/r_winter_projects/master/Birthdays.csv"
csv_url <- "Birthdays.csv"
birthday_data <- read.table(file = csv_url, header = TRUE, sep = ",")
```
