---
title: "Week 2 Assignment"
author: "Sung Lee"
date: "1/9/2020"
output: 
  html_document: 
    df_print: paged
---



[Week 2 Assignment on RPubs](http://rpubs.com/logicalschema/winter_week2 "Sung's Week 2 Assignment Rpubs")
<br>
[Rmd on Github](https://github.com/logicalschema/r_winter_projects/blob/master/week2.Rmd "Sung's week 2 Assignment Github")

``` {r}
require(plyr)

# Load data
# US Births in 1969 - 1988 

z_file <- gzcon(url("https://raw.githubusercontent.com/logicalschema/r_winter_projects/master/Birthdays.csv.gz"))
raw_csv <- textConnection(readLines(z_file))
close(z_file)

birthday_data <- read.table(raw_csv, header = TRUE, sep = ",")
head(birthday_data, 5)
```
<br>
1. Use the summary function to gain an overview of the data set. Then display the mean and median for at least two attributes.

```{r}
summary(birthday_data)
```

###### The mean and median for the year attribute
```{r}
mean(birthday_data$year)
median(birthday_data$year)
```

###### The mean and median for the births attribute
```{r}
mean(birthday_data$births)
median(birthday_data$births)

plot(birthday_data[,c("births", "year")])
```
<br>
2. Create a new data frame with a subset of the columns and rows. Make sure to rename it.
```{r}
subset_birthdays = subset(birthday_data, state == "NY" & year >= 1981 & year <= 1988, select=c(state, year, month, births))

tail(subset_birthdays, 5)
```

<br>
3. Create new column names for the new data frame.

```{r}
subset_birthdays <- rename(subset_birthdays, c("state" = "STATE", "year" = "Y", "month" = "M", "births" = "BIRTHS"))

head(subset_birthdays, 5)
```
<br>
4. Use the summary function to create an overview of your new data frame. Then print the mean and median for the same two attributes. Please compare.

``` {r}
summary(subset_birthdays)
mean(subset_birthdays$Y)
median(subset_birthdays$Y)
mean(subset_birthdays$BIRTHS)
median(subset_birthdays$BIRTHS)
plot(subset_birthdays[,c("BIRTHS", "Y")])
```

The births attribute varied widely from the original data set. The original had a mean: 189 and median: 129. The subset data taken for New York between 1981 and 1988 produced a mean: 709 and median: 711.

<br>
5. For at least 3 values in a column please rename so that every value in that column is renamed. For example, suppose I have 20 values of the letter “e” in one column. Rename those values so that all 20 would show as “excellent”.

The following code replaces `NY` with `New York` and prints out the first hundred rows.

```{r}
subset_birthdays$STATE <- gsub("NY", "New York", subset_birthdays$STATE)

head(subset_birthdays, 100)
```


<br>
6. Display enough rows to see examples of all of steps 1-5 above.


<br>
7. BONUS – place the original .csv in a github file and have R read from the link. This will be a very useful skill as you progress in your data science education and career.

The following code block implements the task. I zipped the csv file to make transport quicker.
```{r eval=FALSE}
z_file <- gzcon(url("https://raw.githubusercontent.com/logicalschema/r_winter_projects/master/Birthdays.csv.gz"))
raw_csv <- textConnection(readLines(z_file))
close(z_file)

birthday_data <- read.table(raw_csv, header = TRUE, sep = ",")
```
